\documentclass{article}

% --- Page geometry (NeurIPS-like: 5.5in text width, 9in text height) ---
\usepackage[
  textwidth=5.5in,
  textheight=9in,
  top=1in,
  left=1.5in,
  headheight=14pt
]{geometry}

% --- Mathematics ---
\usepackage{amsmath,amssymb,amsthm}

% --- Fonts and encoding ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage{microtype}  % disabled: requires full TeX Live

% --- Graphics and figures ---
\usepackage{graphicx}
\graphicspath{{figs/}}

% --- Tables ---
\usepackage{booktabs}

% --- Algorithms (commented: packages not installed in basic TeX Live) ---
% \usepackage{algorithm}
% \usepackage{algorithmic}

% --- Hyperlinks and cross-references ---
\usepackage{hyperref}
\usepackage{url}
% cleveref fallback (package unavailable locally; use \Cref as capitalized \ref)
\newcommand{\Cref}[1]{Section~\ref{#1}}

% --- Colors ---
\usepackage{xcolor}

% --- Natbib for citations ---
\usepackage[numbers,sort&compress]{natbib}

% --- Custom commands ---
\newcommand{\vph}{\varphi}
\newcommand{\Sigr}{\Sigma_r}
\newcommand{\Siga}{\Sigma_{a2}}
\newcommand{\Sigf}[1]{\Sigma_{f#1}}
\newcommand{\Sigs}{\Sigma_{1\to2}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Res}{\mathrm{Res}}

% --- Theorem environments ---
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}

% --- Title ---
\title{Constructing Analytical Solutions for Two-Dimensional\\
Two-Group Neutron Diffusion Equations via\\
Evolutionary Program Synthesis}

\author{
  Author One\thanks{Equal contribution.} \\
  Affiliation \\
  \texttt{author1@email.com} \\
  \and
  Author Two\footnotemark[1] \\
  Affiliation \\
  \texttt{author2@email.com} \\
}

\date{}

\begin{document}
\maketitle

% ============================================================
% Abstract
% ============================================================
\begin{abstract}
Finite difference and finite element solvers for neutron diffusion accumulate discretization error; physics-informed neural networks avoid the mesh but require lengthy training.
%
We take a different route: a Fourier cosine expansion in the transverse direction decouples the two-group neutron diffusion equations into per-mode ODEs whose characteristic equations yield closed-form fast and thermal flux solutions.
%
FaMoU, our LLM-driven evolutionary program synthesis engine, then seeds from this analytical solution and iteratively mutates the solver code, scored by an automated physics evaluator.
%
On a standardized benchmark, the Fourier analytical solution ($N{=}30$ modes) achieves a combined PDE+BC score of $0.9989$, reducing the combined residual 39-fold relative to PINN and surpassing both FDM variants under uniform pointwise evaluation.
An overflow-safe adaptive variant (up to $N{=}221$ modes) reaches $0.9997$.
FaMoU seeds from this solution; after 10 iterations the LLM-evolved program already surpasses the seed, confirming that evolutionary program synthesis is a viable path for physics PDE discovery.
\end{abstract}

% ============================================================
% Main body (modular sections)
% ============================================================
\input{sections/introduction}
\input{sections/related_work}
\input{sections/problem}
\input{sections/method}
\input{sections/experiments}
\input{sections/conclusion}

% ============================================================
% Acknowledgments
% ============================================================
\section*{Acknowledgments}
The authors thank the reviewers for their careful reading. This work was conducted as an independent research project.

% ============================================================
% References
% ============================================================
\bibliographystyle{unsrtnat}
\bibliography{refs}

% ============================================================
% Appendix (optional)
% ============================================================
% \appendix
% \input{sections/appendix}

\end{document}
